---
title: "Serverless providers"
subtitle: "Concurrency to be seen"
author: "Alexander Minyushkin"
date: 2019-03-05T19:00:00+03:00
categories: ["benchmark"]
tags: ["R", "cloud", ]

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
oldw <- getOption("warn")
options(warn = -1)

usePackage <- function(p) {
  if (!is.element(p, installed.packages()[,1]))
    install.packages(p, dep = TRUE)
  require(p, character.only = TRUE, quietly = TRUE)
}

usePackage("data.table") # for fast merging of access log & sar
usePackage("parallel")
usePackage("plyr")
usePackage("ggplot2")

usePackage('DT')
usePackage("plotly")
usePackage("jsonlite")
usePackage("htmltools")

Sys.setlocale("LC_TIME", "us")

options(stringsAsFactors = FALSE)


```

Here is very nice article [The largest benchmark of Serverless providers.](https://medium.com/elbstack/the-largest-benchmark-of-serverless-providers-ac19b55750f4)

And I really wait for new results which was promised to all of us in Bernd's Twitter.

```{r tweet, echo=FALSE}
htmltools::includeHTML("2019-03-05-Serverless-providers_data/tweet.txt")
```




However I found something interesting in previously piblished results.

If we draw actual concurrency during tests we will see that it was not always smooth.

```{r blog, echo=FALSE}



D <- data.table(fromJSON('2019-03-05-Serverless-providers_data/dump.json'))

D <- D[!is.na(fibonacciTime)]

get_concurrency <- function(D, provider_, concurrency_) {
  d<-D[provider == provider_ & concurrency == concurrency_,list(start, end),]

  concurrency <- rbindlist(list(data.table(time = d$start, change= 1), 
                                data.table(time = d$end, change= -1)))[order(time)]
  
  concurrency$time <- concurrency$time - min(concurrency$time)
  
  concurrency <- concurrency[,.(change=sum(change)), "time"]
  concurrency$N <- cumsum(concurrency$change)

  data.table(time = concurrency$time[sort(rep(1:dim(concurrency)[1],2))],
             N = c(0, concurrency$N[sort(rep(1:dim(concurrency)[1],2))[1:(2*dim(concurrency)[1] -1)]]),
             provider = provider_,
             concurrency = concurrency_,
             num_of_tasks = dim(d)[1])
}

all_provider_given_concurrency <- function(D, conc) {
  rbindlist( lapply(unique(D$provider), function(x){get_concurrency(D, x, conc)}))
}

all_concurrency_given_provider <- function(D, prov) {
  rbindlist( lapply(unique(D[provider == prov]$concurrency), function(x){get_concurrency(D, prov, x)}))
}

all_providers_all_concurrency <- function(D) {
  rbindlist( lapply(unique(D$concurrency), 
                    function(x)
                      {all_provider_given_concurrency(D,x)
                      }))
}


  ggplot(data = all_providers_all_concurrency(D[concurrency<60 & concurrency>1]), 
           aes(x=time,
               y=N,
               color=provider,
               group=interaction(provider, concurrency))) +
      geom_line() + ggtitle("Actual Concurrency during execution")
  
```

It looks like GCF had troubles during concurrency=30 test. 

```{r, echo=FALSE}

interactive_plot <-
ggplotly(
  ggplot(data = all_concurrency_given_provider(D[concurrency>1], 'gcf'), 
           aes(x=time,
               y=N,
               color=as.factor(concurrency),
               group=concurrency)) +
      geom_line() + ggtitle("Actual Concurrency during execution. GCF")  
)

interactive_plot

interactive_plot$sizingPolicy$padding <- "0"
htmlwidgets::saveWidget(
  interactive_plot, "../../public/widget/2019-03-05-Serverless-providers_widget.html", libdir = "lib",
  title = "SPEC rint2017 vs rint2006",
  selfcontained = FALSE
)

suppressMessages(ggsave("../../public/widget/2019-03-05-Serverless-providers_widget.png", dpi="screen"))

```

Most likely it is temporary issue, after all they managed to successfully provide concurrency 40 and 50.

How frequently this could happen?

You can leave comments here https://twitter.com/AMiniushkin

